Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-05-24 analysis/paper/paper.Rmd
changes to occurrence, survey access plots

> SECOND graph: [THIS IS SECONDARY PRIORITY] x axis is Time of Day, perhaps broken in to 1 or 2 hour blocks , y axis is ....this is a tough one so totally open to your ideas. How about y axis is % [0, 1.0] and for each year there is a different curve showing the % of planned surveys (as defined above) that were successfully completed that season within that time block; facet by site. So we are seeing whether there are consistently problematic times of day at each site. 
> JOEL: some updates on this! for now, times are in hour blocks. There can't be lines/curves for year since they are unreadable (up/down). I also tried to use color as a factor but then the graphs are crowded (so many years). So I have 2 alternatives, I don't really like either but some are more readable than others. See below.

@@

print(plot_success)
```

```{r Fig-SiteAccess2, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis',fig.height=15, fig.width=12, fig.cap="",warning= FALSE}

print(plot_success3)
```

@@

> MADELEINE: add a graphic of spp frequency of occurrence (maybe some panel-rich figure, one panel per spp, showing annual average percentage of daily observations in which spp was sighted - as line-connected points?- ordered from most frequently observed spp to least frequently. (e.g., use facets). x axis is Day of Season, y axis is % as decimal [0, 1.0], curves for each year; facet by species.
> JOEL: I did some graphs for species occurrence that fit the description but not sure if they were what you were looking for? They do show species occurrence relative to others; as annual/daily percentage of daily observations in which spp was sighted (percentage calculated by annual/daily obs per species over all total obs - is this what you meant? let me know).
Lines didn't work though (lots of ups and downs)

@@

print(plot_occurrenceDay)
```

@@

@@

```{r Covariates, eval=TRUE, cache = FALSE, include = FALSE}
source("../scripts/temp_covariates.R")
```

>>>>

> SECOND graph: [THIS IS SECONDARY PRIORITY] x axis is Time of Day, perhaps broken in to 1 or 2 hour blocks , y axis is ....this is a tough one so totally open to your ideas. How about y axis is % [0, 1.0] and for each year there is a different curve showing the % of planned surveys (as defined above) that were successfully completed that season within that time block; facet by site. So we are seeing whether there are consistently problematic times of day at each site. 
> JOEL: for now, times are in hour blocks

@@

#print(plot_access)
```

@@

> MADELEINE: add a graphic of spp frequency of occurrence (maybe some panel-rich figure, one panel per spp, showing annual average percentage of daily observations in which spp was sighted - as line-connected points?- ordered from most frequently observed spp to least frequently. (e.g., use facets). x axis is Day of Season, y axis is % as decimal [0, 1.0], curves for each year; facet by species.

@@

@@

#print(plot_occurrenceDate)
```

@@

```{r Covariates, eval=TRUE, cache = FALSE, include = FALSE}
#source("../scripts/temp_covariates.R")
```
